Unifying Gompertzian growth with the communicable disease spreading paradigm

### 2022-05-09 elsarticle/elsarticle.tex
update elsarticle and main + figures white background

\documentclass{article}
% \documentclass[review]{elsarticle}

\usepackage{arxiv}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}   % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage[square,numbers]{natbib}
\usepackage{doi}
\usepackage{amsmath}
\usepackage{float}

\newcommand{\insertPdfFig}[3]{
  \begin{figure}[H]
  \centering
  \includegraphics[width=8.4cm]{#1.pdf}
  \caption{#2}
  \label{fig:#1}
  \end{figure}
}

\newcommand{\insertSmallPdfFig}[3]{
  \begin{figure}[h]
  \centering
  \includegraphics[width=8.4cm]{#1.pdf}
  \caption{#2}
  \label{fig:#1}
  \end{figure}
}

% \title{On the nature of the Gompertz in relation to the epidemic in 2019-2021}
\title{Unifying Gompertzian growth with the communicable disease spreading paradigm}
\graphicspath{{figures/}}
%\date{September 9, 1985} % Here you can change the date presented in the paper title
%\date{}          % Or removing it

\author{Matz A. Haugen, \\
Independent Reseacher, Oslo\\
\texttt{matzhaugen@gmail.com} \\
  \And
  Dorothea Gilbert \\
  University of Oslo\\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

% Uncomment to remove the date
%\date{}

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{On the nature of the Gompertz}

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={A template for the arxiv style},
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={Matz A. Haugen},
pdfkeywords={},
}

\begin{document}
\maketitle

@@

% keywords can be removed
\keywords{Gompertz \and Coherence \and Covid \and Coronavirus \and Network Analysis \and Stochastic}

\section{Introduction}
Traditional communicable disease spreading theory assumes a pathogen which infects the population through a network of transmission. 
Following this line of reasoning it can be theoretically shown that in the early stages of an epidemic, growth follows a logistic-like curve, where the very beginning exhibits exponential growth, and for which analytic and semi-analytic solutions have recently emerged \citep{harko2014exact,kroger2020analytical,schlickeiser2021analytical,heng2020approximately}. 
A large body of research has emerged that explores how these models fit the recent mortality seen due to the Coronavirus epidemic \citep{carletti2020covid,cooper2020sir,postnikov2020estimation,munoz2021sir,cooper2022dynamical,saikia2021covid}.

@@

\section*{Code Availability}
The computer code required to produce the results are given in the following Github repository,
\begin{verbatim}
https://github.com/matzhaugen/GompertzManuscript
\end{verbatim}

\newpage

@@

\subsection{A note on estimation}

% Estimating the parameters using real data requires some consideration around the variance of the growth variable as a function of time. This variance will in turn inform the estimation process by considering a weighted minimization of the residuals of the observations regressed onto the model. In the stochastic Gompertz process postulated in Section \ref{seq:alt}, the process under a log-transformation is the Ornstein-Uhlenbeck process which has a closed from expression for its transition probability, and thus its variance as a function of time. This variance can then be used in a weighted least squares estimation technique or any other weighted technique. In the original domain there is also a closed form expression available but it is somewhat more convoluted and given that observations in this domain are visually quite homoscedastic with equal variance across time (Fig \ref{fig:Gompertz_vs_SIRD} and Tables \ref{tab:gomp} and \ref{tab:sird}), this is expression and consideration is omitted. But for the log-domain, observations exibit changing variance with time.

% To be explicit, if we consider the notation from Section \ref{seq:alt} and let $P(z, t|z', t')$ be the transition probability from some growth and time coordinate $z', t'$ to some other growth and time coordinate $z, t$, than the transition probability of the Olstein-Uhlenbeck process in \ref{eq:microscopic} is given by\citep{risken1996fokker},
% \begin{equation}
% P(z, t|z', t') = \sqrt{\frac{\beta}{2\pi \sigma (1 - e^{-2\beta (t-t')})}}\exp{\left[ -\frac{\beta (z - e^{-\beta(t-t')}z')^2}{2\sigma(1-e^{-2 \beta(t-t')})} \right]}.
% \end{equation}

% If we consider $t$ the time at which the stationary distribution is reached and that this stationary distribution is given as a delta function, variance of the growth will be given as
% \begin{equation}
% \text{Var[Z(t)|t']} = \sigma(1-e^{-2 \beta(t-t')}).
% \end{equation}

% Because weights on observations in a regression are invariant to multiplication we can let $\sigma=1$. The slope coefficient would have to be estimated either by a standard least squares or through the 3-parameter model in (\ref{eq:GompertzODE}).

The time-evolution of the SIRD and the Gompertz model are obtained with a Runge-Kutta (4) algorithm, after first fitting parameters using non-linear least squares according to equations (\ref{eq:GompertzODE}) and (\ref{eq:SIRD_D}) in the text (Fig. \ref{fig:Gompertz_vs_SIRD}). Fitting is done with Python-Scipy and a 6-day windowed average of deaths. Observations are taken from the Github repository compiled by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University, Baltimore, USA \citep{dong2020interactive}.

The transmission rate is modeled as the product of $\eta \xi$ is (\ref{eq:SIRD_D}), and its associated variance is obtained assuming a bi-normal relationship between the two parameters with cross-correlation $\rho$ \citep{nadarajah2016distribution},
\begin{equation}
\text{Var}[\beta] = \text{Var}[\eta] \text{Var}[\xi] (1 + \rho^2) + \text{Var}[\xi]*\eta^2 + \text{Var}[\eta] \xi^2.
\end{equation}

\insertPdfFig{Gompertz_vs_SIRD}{Cumulative diseased plotted against number of days after $Y(t) / Y_{max}>0.005$, comparing an SIRD with a Gompertz model. Both models are fit using non-linear least squares according to equations (\ref{eq:GompertzODE}) and (\ref{eq:SIRD_D}) in the text.}

% \insertPdfFig{Gompertz_vs_SIRD_gompfit_log_domain}{Log transformed cumulative diseased plotted against its time derivative after $Y(t) / Y_{max}>0.005$, with a straight line fit regressing onto the $50^{th}$ quantile.}

@@

\begin{table}[H]
\label{tab:gomp}
\centering
\caption{Estimated values for the Gompertz model fitted to various countries' observations, as shown in Figure \ref{fig:Gompertz_vs_SIRD_lnln_infty} using notation from \ref{eq:GompertzODE}.}
\begin{tabular}{llll}
\toprule
{} &             $\nu\times 10$ &           $\beta\times 10^{2}$ &        $\tilde{Y}\times 10^{2}$ \\
\midrule
Belgium        &   9.3(1) &   8.1(2) &  10.1(9) \\
Portugal       &  6.15(3) &  6.22(7) &   7.0(3) \\
Austria        &  7.28(7) &   8.1(2) &   8.1(7) \\
Switzerland    &  8.08(6) &   8.1(1) &   8.9(5) \\
Sweden         &   4.9(1) &   4.3(2) &     6(1) \\
Italy          &  7.60(6) &  5.88(7) &   8.4(4) \\
France         &  10.2(1) &   8.2(1) &  11.0(8) \\
Spain          &  9.41(9) &   7.5(1) &  10.2(7) \\
Germany        &  7.56(6) &  6.53(8) &   8.4(4) \\
Denmark        &  5.94(7) &   6.5(2) &   6.8(7) \\
United Kingdom &  8.46(5) &  6.54(7) &   9.3(4) \\
Netherlands    &  7.34(6) &  6.52(8) &   8.2(4) \\
Turkey         &  7.04(5) &  6.38(8) &   7.9(4) \\
Iran           &  5.87(6) &  5.04(8) &   6.7(4) \\
US             &  7.53(7) &  5.32(7) &   8.4(5) \\
China          &   9.8(1) &   9.4(2) &    10(1) \\
\bottomrule
\end{tabular}

\end{table}
\bibliographystyle{plainnat}
\bibliography{references2}  %%% Uncomment this line and comment out the ``thebibliography'' section below to use the external .bib file (using bibtex) .

%%% Uncomment this section and comment out the \bibliography{references} line above to use inline references.
% \begin{thebibliography}{1}

%   \bibitem{kour2014real}
%   George Kour and Raid Saabne.
%   \newblock Real-time segmentation of on-line handwritten arabic script.
%   \newblock In {\em Frontiers in Handwriting Recognition (ICFHR), 2014 14th
%       International Conference on}, pages 417--422. IEEE, 2014.

%   \bibitem{kour2014fast}
%   George Kour and Raid Saabne.
%   \newblock Fast classification of handwritten on-line arabic characters.
%   \newblock In {\em Soft Computing and Pattern Recognition (SoCPaR), 2014 6th
%       International Conference of}, pages 312--318. IEEE, 2014.

%   \bibitem{hadash2018estimate}
%   Guy Hadash, Einat Kermany, Boaz Carmeli, Ofer Lavi, George Kour, and Alon
%   Jacovi.
%   \newblock Estimate and replace: A novel approach to integrating deep neural
%   networks with existing applications.
%   \newblock {\em arXiv preprint arXiv:1804.09028}, 2018.

% \end{thebibliography}

>>>>

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{float}
\usepackage{booktabs}       % professional-quality tables
\usepackage{graphicx}
\modulolinenumbers[5]

\journal{Chaos, Solitons \& Fractals}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
% \bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
% \bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\insertPdfFig}[3]{
  \begin{figure}[H]
  \centering
  \includegraphics[width=12.4cm]{#1.pdf}
  \caption{#2}
  \label{fig:#1}
  \end{figure}
}

\newcommand{\insertSmallPdfFig}[3]{
  \begin{figure}[h]
  \centering
  \includegraphics[width=8.4cm]{#1.pdf}
  \caption{#2}
  \label{fig:#1}
  \end{figure}
}
\graphicspath{{../figures/}}
\begin{document}

\begin{frontmatter}

\title{Unifying Gompertzian growth with the communicable disease spreading paradigm}

%% Group authors per affiliation:
% \author{Matz Andreas Haugen\fnref{myfootnote}}
% \address{Enerhauggata 1, 0651 Oslo, Norway}
% \fntext[myfootnote]{Since 1880.}

%% or include affiliations in footnotes:
\author[mymainaddress]{Matz Andreas Haugen\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
% \ead[url]{www.matzhaugen.com}
\ead{matzhaugen@gmail.com}

\author[mysecondaryaddress]{Dorothea Gilbert}

\address[mymainaddress]{Enerhauggata 1, 0651 Oslo, Norway}
\address[mysecondaryaddress]{University of Oslo, Oslo, Norway}

@@

\begin{keyword}
Gompertz \sep Coherence \sep Covid \sep Coronavirus \sep Network Analysis \sep Stochastic
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}

Traditional communicable disease spreading theory assumes a pathogen which infects the population through a network of transmission. 
Following this line of reasoning it can be theoretically shown that in the early stages of an epidemic, growth follows a logistic-like curve, where the very beginning exhibits exponential growth, and for which analytic and semi-analytic solutions have recently emerged \citep{harko2014exact,kroger2020analytical,schlickeiser2021analytical,heng2020approximately}. 
A large body of research has emerged that explores how these models fit the recent mortality seen due to the Coronavirus epidemic \citep{carletti2020covid,cooper2020sir,postnikov2020estimation,munoz2021sir,cooper2022dynamical,saikia2021covid}.

@@

\section*{Methods}

\subsection{Estimating model parameters}
The time-evolution of the SIRD and the Gompertz model are obtained with a Runge-Kutta algorithm, after first fitting parameters using non-linear least squares according to equations (\ref{eq:GompertzODE}) and (\ref{eq:SIRD_D}) in the text (Fig. \ref{fig:Gompertz_vs_SIRD}). Fitting is done with Python-Scipy with specified Jacobians and a 6-day windowed average of observed deaths. Observations are taken from the Github repository compiled by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University, Baltimore, USA \citep{dong2020interactive}.

The transmission rate is modeled as the product of $\eta \xi$ in (\ref{eq:SIRD_D}), and its associated variance is obtained assuming a bi-normal relationship between the two parameters with cross-correlation $\rho$ \citep{nadarajah2016distribution},
\begin{equation}
\text{Var}[\beta] = \text{Var}[\eta] \text{Var}[\xi] (1 + \rho^2) + \text{Var}[\xi]*\eta^2 + \text{Var}[\eta] \xi^2.
\end{equation}

\subsection{Code Availability}
The computer code required to produce the results are given in the following Github repository,
\begin{verbatim}
https://github.com/matzhaugen/GompertzManuscript
\end{verbatim}

@@

\insertPdfFig{Gompertz_vs_SIRD}{Cumulative diseased plotted against number of days after $Y(t) / Y_{max}>0.005$, comparing an SIRD with a Gompertz model. Both models are fit using non-linear least squares according to equations (\ref{eq:GompertzODE}) and (\ref{eq:SIRD_D}) in the text. Fitting is done with Python-Scipy and a 6-day windowed average of deaths. Observations are taken from the Github repository compiled by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University, Baltimore, USA \citep{dong2020interactive}.}

@@

\begin{table}[H]
\label{tab:gomp}
\centering
\caption{Estimated values for the Gompertz model fitted to various countries' observations, as shown in Figure \ref{fig:Gompertz_vs_SIRD_lnln_infty} using notation from \ref{eq:GompertzODE}. Standard deviation estimates is given in the paranthesis corresponding to the last significant digit of the reported number.}
\begin{tabular}{llll}
\toprule
{} &             $\nu\times 10$ &           $\beta\times 10^{2}$ &        $\tilde{Y}\times 10^{2}$ \\
\midrule
Belgium        &   9.3(1) &   8.1(2) &  10.1(9) \\
Portugal       &  6.15(3) &  6.22(7) &   7.0(3) \\
Austria        &  7.28(7) &   8.1(2) &   8.1(7) \\
Switzerland    &  8.08(6) &   8.1(1) &   8.9(5) \\
Sweden         &   4.9(1) &   4.3(2) &     6(1) \\
Italy          &  7.60(6) &  5.88(7) &   8.4(4) \\
France         &  10.2(1) &   8.2(1) &  11.0(8) \\
Spain          &  9.41(9) &   7.5(1) &  10.2(7) \\
Germany        &  7.56(6) &  6.53(8) &   8.4(4) \\
Denmark        &  5.94(7) &   6.5(2) &   6.8(7) \\
United Kingdom &  8.46(5) &  6.54(7) &   9.3(4) \\
Netherlands    &  7.34(6) &  6.52(8) &   8.2(4) \\
Turkey         &  7.04(5) &  6.38(8) &   7.9(4) \\
Iran           &  5.87(6) &  5.04(8) &   6.7(4) \\
US             &  7.53(7) &  5.32(7) &   8.4(5) \\
China          &   9.8(1) &   9.4(2) &    10(1) \\
\bottomrule
\end{tabular}

% \section*{References}

\bibliography{../references2}

### 2022-05-09 main.tex
update elsarticle and main + figures white background

\section*{Code Availability}
The computer code required to produce the results are given in the following Github repository,
\begin{verbatim}
https://github.com/matzhaugen/GompertzManuscript
\end{verbatim}

@@

@@

The time-evolution of the SIRD and the Gompertz model are obtained with a Runge-Kutta (4) algorithm, after first fitting parameters using non-linear least squares according to equations (\ref{eq:GompertzODE}) and (\ref{eq:SIRD_D}) in the text (Fig. \ref{fig:Gompertz_vs_SIRD}). Fitting is done with Python-Scipy and a 6-day windowed average of deaths. Observations are taken from the Github repository compiled by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University, Baltimore, USA \citep{dong2020interactive}.

The transmission rate is modeled as the product of $\eta \xi$ is (\ref{eq:SIRD_D}), and its associated variance is obtained assuming a bi-normal relationship between the two parameters with cross-correlation $\rho$ \citep{nadarajah2016distribution},
\begin{equation}
\text{Var}[\beta] = \text{Var}[\eta] \text{Var}[\xi] (1 + \rho^2) + \text{Var}[\xi]*\eta^2 + \text{Var}[\eta] \xi^2.
\end{equation}

\insertPdfFig{Gompertz_vs_SIRD}{Cumulative diseased plotted against number of days after $Y(t) / Y_{max}>0.005$, comparing an SIRD with a Gompertz model. Both models are fit using non-linear least squares according to equations (\ref{eq:GompertzODE}) and (\ref{eq:SIRD_D}) in the text.}

@@

\begin{table}[H]
\label{tab:sird}
\centering
\caption{Estimated values for the SIRD model fitted to various countries' observations as shown in Figure \ref{fig:Gompertz_vs_SIRD_lnln_infty} using notation from \ref{eq:SIRD_D}. Standard deviation is given in the paranthesis corresponding to the last significant digit of the reported number.}
\begin{tabular}{llll}
\toprule
{} &           $\eta\times 10^{-1}$ &      $\xi \times 10^{4}$ &            $\kappa\times 10^{2}$ \\
\midrule
Belgium        &    94(8) &   3.2(2) &   9.3(7) \\
Portugal       &   6.6(4) &    35(2) &   4.5(3) \\
Austria        &     8(1) &    36(5) &    11(1) \\
Switzerland    &    22(1) &  13.6(7) &  11.0(5) \\
Sweden         &    19(5) &     8(2) &     3(1) \\
Italy          &   137(3) &  1.77(5) &  3.71(1) \\
France         &  240(10) &  1.24(7) &   8.1(4) \\
Spain          &   145(2) &  2.27(5) &  4.75(8) \\
Germany        &    61(4) &   3.9(3) &   6.5(5) \\
Denmark        &   2.7(2) &    96(8) &   4.3(3) \\
United Kingdom &   181(5) &  1.39(5) &   4.3(1) \\
Netherlands    &    29(1) &   8.9(5) &   4.3(2) \\
Turkey         &    34(3) &   6.8(5) &   6.9(6) \\
Iran           &  22.3(4) &  10.4(4) &  2.51(7) \\
US             &   312(5) &  0.76(2) &  1.83(7) \\
China          &  130(30) &   3.5(5) &    26(4) \\
\bottomrule
\end{tabular}

@@

\end{table}
\bibliographystyle{plainnat}
\bibliography{references2}  %%% Uncomment this line and comment out the ``thebibliography'' section below to use the external .bib file (using bibtex) .

>>>>

@@

\section*{Methods}

\subsection{Estimating model parameters}
The time-evolution of the SIRD and the Gompertz model are obtained with a Runge-Kutta algorithm, after first fitting parameters using non-linear least squares according to equations (\ref{eq:GompertzODE}) and (\ref{eq:SIRD_D}) in the text (Fig. \ref{fig:Gompertz_vs_SIRD}). Fitting is done with Python-Scipy with specified Jacobians and a 6-day windowed average of observed deaths. Observations are taken from the Github repository compiled by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University, Baltimore, USA \citep{dong2020interactive}.

The transmission rate is modeled as the product of $\eta \xi$ in (\ref{eq:SIRD_D}), and its associated variance is obtained assuming a bi-normal relationship between the two parameters with cross-correlation $\rho$ \citep{nadarajah2016distribution},
\begin{equation}
\text{Var}[\beta] = \text{Var}[\eta] \text{Var}[\xi] (1 + \rho^2) + \text{Var}[\xi]*\eta^2 + \text{Var}[\eta] \xi^2.
\end{equation}

\subsection{Code Availability}
The computer code required to produce the results are given in the following Github repository,
\begin{verbatim}
https://github.com/matzhaugen/GompertzManuscript
\end{verbatim}

@@

\insertPdfFig{Gompertz_vs_SIRD}{Cumulative diseased plotted against number of days after $Y(t) / Y_{max}>0.005$, comparing an SIRD with a Gompertz model. Both models are fit using non-linear least squares according to equations (\ref{eq:GompertzODE}) and (\ref{eq:SIRD_D}) in the text. Fitting is done with Python-Scipy and a 6-day windowed average of deaths. Observations are taken from the Github repository compiled by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University, Baltimore, USA \citep{dong2020interactive}.}

@@

\begin{table}[H]
\label{tab:sird}
\centering
\caption{Estimated values for the SIRD model fitted to various countries' observations as shown in Figure \ref{fig:Gompertz_vs_SIRD_lnln_infty} using notation from \ref{eq:SIRD_D}. Standard deviation estimates is given in the paranthesis corresponding to the last significant digit of the reported number.}
\begin{tabular}{llll}
\toprule
{} &           $\eta\times 10^{-1}$ &      $\xi \times 10^{4}$ &            $\kappa\times 10^{2}$ \\
\midrule
Belgium        &    94(8) &   3.2(2) &   9.3(7) \\
Portugal       &   6.6(4) &    35(2) &   4.5(3) \\
Austria        &     8(1) &    36(5) &    11(1) \\
Switzerland    &    22(1) &  13.6(7) &  11.0(5) \\
Sweden         &    19(5) &     8(2) &     3(1) \\
Italy          &   137(3) &  1.77(5) &  3.71(1) \\
France         &  240(10) &  1.24(7) &   8.1(4) \\
Spain          &   145(2) &  2.27(5) &  4.75(8) \\
Germany        &    61(4) &   3.9(3) &   6.5(5) \\
Denmark        &   2.7(2) &    96(8) &   4.3(3) \\
United Kingdom &   181(5) &  1.39(5) &   4.3(1) \\
Netherlands    &    29(1) &   8.9(5) &   4.3(2) \\
Turkey         &    34(3) &   6.8(5) &   6.9(6) \\
Iran           &  22.3(4) &  10.4(4) &  2.51(7) \\
US             &   312(5) &  0.76(2) &  1.83(7) \\
China          &  130(30) &   3.5(5) &    26(4) \\
\bottomrule
\end{tabular}

@@

\end{table}
\bibliographystyle{abbrvnat}
\bibliography{references2}  %%% Uncomment this line and comment out the ``thebibliography'' section below to use the external .bib file (using bibtex) .
